Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-15 paper/paper.tex
nudges

\item We design and implement an automatic approach in a tool called \tool  
  for generating {\em correct-by-construction} digital controllers that is
  based on state-of-the-art inductive synthesis techniques.  Our application
  of program synthesis is non-trivial and requires addressing challenges
  specific to embedded control systems, such as the effects of quantizers
  and FWL.  In particular, we have found that a two-stage verification
  engine that continuously refines the precision of the fixed-point
  representation of the plant is key to the performance of our approach
  yielding, in most cases, a speed-up of at least two orders of magnitude
  over a conventional one-stage verification engine.

>>>>

\item We design and implement an automatic approach in our tool \tool  
  for generating {\em correct-by-construction} digital controllers that is
  based on state-of-the-art inductive synthesis techniques.  Our application
  of program synthesis is non-trivial and requires addressing challenges
  specific to embedded control systems, such as the effects of quantizers
  and FWL.  In particular, we have found that a two-stage verification
  engine that continuously refines the precision of the fixed-point
  representation of the plant is key to the performance of our approach
  yielding, in most cases, a speed-up of at least two orders of magnitude
  over a conventional one-stage verification engine.
